### 2022-01-04 manuscript.tex
Fix ref [ci skip]
This build is based on
https://github.com/lubianat/quali_phd/commit/f962072fcd0685f369693089c4c2d0b96e523fd1.

This commit was created by the following CI build and job:
https://github.com/lubianat/quali_phd/commit/f962072fcd0685f369693089c4c2d0b96e523fd1/checks
https://github.com/lubianat/quali_phd/actions/runs/1655118311

This manuscript
(\href{https://lubianat.github.io/quali_phd/v/851295e93a8879e9354aca9a13f1b9884a7be405/}{permalink})
was automatically generated
from \href{https://github.com/lubianat/quali_phd/tree/851295e93a8879e9354aca9a13f1b9884a7be405}{lubianat/quali\_phd@851295e}
on December 15, 2021.

@@

Information on Wikidata is released under a CC0 license, which enables full reuse of the data. {[}\protect\hyperlink{ref-tQIJPG4k}{86}{]}
One of the major points of access and reuse of the information is the Wikidata Query Service {[}\protect\hyperlink{ref-2wDsXBwd}{87}{]}, a core resource of the community which enables live querying in the SPARQL language. {[}\protect\hyperlink{ref-t66jYhqe}{88}{]}
A number of services make use of embedded queries from the Wikidata Query Service {[}\protect\hyperlink{ref-2wDsXBwd}{87}{]} to create interactive, live dashboards like Scholia {[}\protect\hyperlink{ref-17P4zruFZ}{89}{]} and the SARS-CoV-2 Query Book {[}\protect\hyperlink{ref-guMp3q1V}{90}{]}

@@

Making the Human Cell Atlas more useful via Wikidata also includes the connection of related databases.
PanglaoDB {[}\protect\hyperlink{ref-M0lqRYJb}{134}{]} {[}\protect\hyperlink{ref-T3PlZ3Vh}{135}{]} is a publically-available database that contains data and metadata on hundreds of single-cell RNA sequencing experiments.
It provides extensive information on cell types, genes, tissues, and cell type markers, obtained via automatic and manual methods.
It also displays a rich web user interface for easy data acquisition, including database dumps for bulk downloads.

As of 8 December June 2021, the article describing PanglaoDB had been cited 230 times.
Despite its use by the community, the database is on a 3-star category for Linked Open Data {[}\protect\hyperlink{ref-OGXYtGZ8}{136}{]} as it does not use the open semantic standards from W3C (RDF and SPARQL) needed for a 4-star rank, neither the links to external data via standard identifiers that make datasets 5-star.
Improving the data format toward W3C's gold standards is a valuable step in making biological knowledge FAIR (Findable, Accessible, Interoperable, and Reusable).
Thus, we aimed to provide a case study of making the core information of PandlaoDB available in a 5-star Linked Open Data Format while improving the modelling of the necessary concepts on Wikidata.

As of August 2020, Wikidata had 264 items categorized as a ``cell type'', considerably less than in specialized cell catalogues, which count over two thousand cell types {[}\protect\hyperlink{ref-agnqfdk6}{52},\protect\hyperlink{ref-4AEy2xhQ}{137}{]}.
Strikingly, there were also 23 items categorized as instances of ``cell (Q7868)''.
This classification is imprecise, as an instance of cell would be an individual named cell from a single named individual, an example of conceptual disarray that often occurs on Wikidata. {[}\protect\hyperlink{ref-imSZTi52}{138}{]}

Wikidata editors often mix 1st-order classes such as ``cells'' and ``organs'' with metaclasses like ``cell types'' and ``organ types''.
As mentioned in the chapter on the concept of cell type, individuals, like the ``Dolly sheep zygote'' (a real-world ``cell'') and the ``brain of Albert Einstein'' (a real-world ``organ'') are instances of classes.
Classes, like ``zygote'' (a conceptual ``cell type'') and ``brain'' (a conceptual ``organ type'') are instances of \emph{metaclasses}.

@@

Classes corresponding to species-neutral classes were retrieved from Wikidata manually using Wikidata's Graphic User Interface.
A manually-curated dictionary matching terms in PanglaoDB to Wikidata identifiers was assembled and used for integration.
Cell types that were not represented on Wikidata were added to the database via the graphical user interface (\url{https://www.wikidata.org/wiki/Special:NewItem}) and logged in the reference table.

@@

\hypertarget{results}{%
\subsubsection{Results}\label{results}}

@@

Besides integration with Gene Ontology, Wikidata reconciliation makes it possible to complement the marker gene info on PanglaoDB with information about diseases. This integration is of biomedical interest, as there is a quest to detail mechanisms that link genetic associations and the diseases themselves.

``Disease genes'' are often compiled from Genomic Wide Association Studies, which look for sequence variation in the DNA. These studies are commonly blind to the cell types related to the pathophysiology of the disease. In the query below, we can see cell types marked by genes genetically associated with Parkinson's disease. Even considering the false positives, the overview can aid domain experts in coming up with novel hypotheses.

@@

The reading framework of Wikidata bib is built upon a git repository integrated with GitHub, Python3 scripts and SPARQL queries.
It has a standard file structure, summarized as the following:

@@

The next years of study will be devoted to improving the projects presented here into mature, useful objects.
We hope to improve the interplay of Wikidata and Cell Ontology, developing frameworks to combine community- and expert-based curation of knowledge on cell types.
Furthermore, we plan to integrate Wikidata to current single-cell RNA-sequencing pipelines by adapting R packages to use Wikidata (e.g.~the ontology-based packages OnClass {[}\protect\hyperlink{ref-sW6aNZJB}{56}{]} and ontoProc{[}\protect\hyperlink{ref-15YmDXALp}{57}{]}) .
Finally, we aim at moving the Wikidata Bib system to a well documented, user-friendly mature system, testing usability with other academics and distributing it as a durable open-source project.

@@

\begin{itemize}
\tightlist
\item
  (Feb-2021) Presented an open talk at the ``Semana da Bioinformática'' event about modelling of biological systems (1020 views as of December 2021) {[}\protect\hyperlink{ref-url}{\textbf{url?}}``https://www.youtube.com/watch?v=VDvCxskIGEI''{]}
\item
  (Jun-Aug 2021) Helped to organize the No-Budget-Science HackWeek virtual hackathon {[}\protect\hyperlink{ref-12LOzmXRs}{164}{]}
\item
  (Jul - 2021) Presented the work ``Wikidata for 5-star Linked Open Databases: A case study of PanglaoDB'' at the Bio-Ontologies section of the Annual International Conference on Intelligent Systems for Molecular Biology. {[}\protect\hyperlink{ref-SALI6Ywb}{165}{]}. The presentation was awarded the best
\item
  (Jul - 2021) Awarded the 2nd place in the International Society for Computational Biology (ISCB) Wikipedia Competition for the contributions to the Wikipedia page on Biocuration (\url{https://en.wikipedia.org/wiki/Biocuration}) {[}\protect\hyperlink{ref-IJG65hFm}{166}{]}
\item
  (Nov - 2021) Managed a project during BioHackathon Europe 2021, in Barcelona, Spain, on the representation of ELIXIR information on Wikidata. {[}\protect\hyperlink{ref-14Wi842eZ}{167}{]}
\end{itemize}

@@

\leavevmode\vadjust pre{\hypertarget{ref-ogAGO9KH}{}}%
\CSLLeftMargin{33. }
\CSLRightInline{\textbf{The origin and evolution of cell types}
\CSLBlock{Detlev Arendt, Jacob M Musser, Clare VH Baker, Aviv Bergman, Connie Cepko, Douglas H Erwin, Mihaela Pavlicev, Gerhard Schlosser, Stefanie Widder, Manfred D Laubichler, Günter P Wagner} \emph{Nature Reviews Genetics} (2016-11-07) \url{https://doi.org/f9b62x}
\CSLBlock{DOI: \href{https://doi.org/10.1038/nrg.2016.127}{10.1038/nrg.2016.127} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27818507}{27818507}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-g74dZjOM}{}}%
\CSLLeftMargin{38. }
\CSLRightInline{\textbf{Species Concepts and Species Delimitation}
\CSLBlock{Kevin De Queiroz} \emph{Systematic Biology} (2007-12) \url{https://doi.org/c34kzf}
\CSLBlock{DOI: \href{https://doi.org/10.1080/10635150701701083}{10.1080/10635150701701083} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/18027281}{18027281}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-gAysgnsS}{}}%
\CSLLeftMargin{40. }
\CSLRightInline{\textbf{Logical Development of the Cell Ontology}
\CSLBlock{Terrence F Meehan, Anna Maria Masci, Amina Abdulla, Lindsay G Cowell, Judith A Blake, Christopher J Mungall, Alexander D Diehl} \emph{BMC Bioinformatics} (2011-01-05) \url{https://doi.org/c7kw6x}
\CSLBlock{DOI: \href{https://doi.org/10.1186/1471-2105-12-6}{10.1186/1471-2105-12-6} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/21208450}{21208450} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3024222}{PMC3024222}}}

\leavevmode\vadjust pre{\hypertarget{ref-17U3pGEjv}{}}%
\CSLLeftMargin{41. }
\CSLRightInline{\textbf{The Cell Ontology 2016: enhanced content, modularization, and ontology interoperability}
\CSLBlock{Alexander D Diehl, Terrence F Meehan, Yvonne M Bradford, Matthew H Brush, Wasila M Dahdul, David S Dougall, Yongqun He, David Osumi-Sutherland, Alan Ruttenberg, Sirarat Sarntivijai, \ldots{} Christopher J Mungall} \emph{Journal of Biomedical Semantics} (2016-07-04) \url{https://doi.org/gg99b9}
\CSLBlock{DOI: \href{https://doi.org/10.1186/s13326-016-0088-7}{10.1186/s13326-016-0088-7} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27377652}{27377652} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4932724}{PMC4932724}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-jX2ZmXcc}{}}%
\CSLLeftMargin{43. }
\CSLRightInline{\textbf{Cells in experimental life sciences - challenges and solution to the rapid evolution of knowledge}
\CSLBlock{Sirarat Sarntivijai, Alexander D Diehl, Yongqun He} \emph{BMC Bioinformatics} (2017-12-21) \url{https://doi.org/gg99b7}
\CSLBlock{DOI: \href{https://doi.org/10.1186/s12859-017-1976-2}{10.1186/s12859-017-1976-2} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29322916}{29322916} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5763506}{PMC5763506}}}

\leavevmode\vadjust pre{\hypertarget{ref-rK8KD0us}{}}%
\CSLLeftMargin{44. }
\CSLRightInline{\textbf{Cells in ExperimentaL Life Sciences (CELLS-2018): capturing the knowledge of normal and diseased cells with ontologies}
\CSLBlock{Sirarat Sarntivijai, Yongqun He, Alexander D Diehl} \emph{BMC Bioinformatics} (2019-04-25) \url{https://doi.org/gg99b8}
\CSLBlock{DOI: \href{https://doi.org/10.1186/s12859-019-2721-9}{10.1186/s12859-019-2721-9} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31272374}{31272374} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6509796}{PMC6509796}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-t66jYhqe}{}}%
\CSLLeftMargin{88. }
\CSLRightInline{\href{https://Q56010228}{Q56010228}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-P1EnNa7Q}{}}%
\CSLLeftMargin{110. }
\CSLRightInline{\textbf{The LOTUS Initiative for Open Natural Products Research: Knowledge Management through Wikidata}
\CSLBlock{Adriano Rutz, Maria Sorokina, Jakub Galgonek, Daniel Mietchen, Egon Willighagen, Arnaud Gaudry, James G Graham, Ralf Stephan, Roderic Page, Jiří Vondrášek, \ldots{} Pierre-Marie Allard} \emph{Cold Spring Harbor Laboratory} (2021-05-28) \url{https://doi.org/gh6dqk}
\CSLBlock{DOI: \href{https://doi.org/10.1101/2021.02.28.433265}{10.1101/2021.02.28.433265}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-uCE45Jh8}{}}%
\CSLLeftMargin{127. }
\CSLRightInline{\textbf{Towards a pragmatic definition of cell type}
\CSLBlock{Tiago Lubiana, Helder I Nakaya} \emph{Authorea, Inc.} (2021-01-04) \url{https://doi.org/ghrxwf}
\CSLBlock{DOI: \href{https://doi.org/10.22541/au.160979530.02627436/v1}{10.22541/au.160979530.02627436/v1}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-T3PlZ3Vh}{}}%
\CSLLeftMargin{135. }
\CSLRightInline{\textbf{PanglaoDB: a web server for exploration of mouse and human single-cell RNA sequencing data}
\CSLBlock{Oscar Franzén, Li-Ming Gan, Johan LM Björkegren} \emph{Database} (2019) \url{https://doi.org/ggkzxr}
\CSLBlock{DOI: \href{https://doi.org/10.1093/database/baz046}{10.1093/database/baz046} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/30951143}{30951143} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6450036}{PMC6450036}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-MxIeSJYt}{}}%
\CSLLeftMargin{156. }
\CSLRightInline{\textbf{fcoex: FCBF-based Co-Expression Networks for Single Cells}
\CSLBlock{Tiago Lubiana, Helder Nakaya} \emph{Bioconductor version: Release (3.14)} (2021) \url{https://bioconductor.org/packages/fcoex/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-oXMFSv5v}{}}%
\CSLLeftMargin{161. }
\CSLRightInline{\textbf{Sharing intermediate datasets from systematic reviews}
\CSLBlock{Tiago Lubiana, Olavo Bohrer Amaral, Kleber Neves} \emph{Center for Open Science} (2021-11-29) \url{https://doi.org/gnrf9v}
\CSLBlock{DOI: \href{https://doi.org/10.31222/osf.io/vbwa9}{10.31222/osf.io/vbwa9}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-SALI6Ywb}{}}%
\CSLLeftMargin{165. }
\CSLRightInline{\textbf{Wikidata for 5-star Linked Open Databases: A case study of PanglaoDB}
\CSLBlock{Tiago Lubiana, João Vitor Ferreira Cavalcante} \emph{Zenodo} (2021-12-01) \url{https://doi.org/gnpzvr}
\CSLBlock{DOI: \href{https://doi.org/10.5281/zenodo.5747849}{10.5281/zenodo.5747849}}}

\leavevmode\vadjust pre{\hypertarget{ref-IJG65hFm}{}}%
\CSLLeftMargin{166. }
\CSLRightInline{\textbf{Biocuration - Wikipedia} \url{https://en.wikipedia.org/wiki/Biocuration}}

\leavevmode\vadjust pre{\hypertarget{ref-14Wi842eZ}{}}%
\CSLLeftMargin{167. }
\CSLRightInline{\textbf{biohackathon-projects-2021/projects/32 at main · elixir-europe/biohackathon-projects-2021}
\CSLBlock{GitHub} \url{https://github.com/elixir-europe/biohackathon-projects-2021}}

>>>>

This manuscript
(\href{https://lubianat.github.io/quali_phd/v/f962072fcd0685f369693089c4c2d0b96e523fd1/}{permalink})
was automatically generated
from \href{https://github.com/lubianat/quali_phd/tree/f962072fcd0685f369693089c4c2d0b96e523fd1}{lubianat/quali\_phd@f962072}
on January 4, 2022.

@@

Information on Wikidata is released under a CC0 license, which enables full reuse of the data. {[}\protect\hyperlink{ref-tQIJPG4k}{86}{]}
One of the major points of access and reuse of the information is the Wikidata Query Service {[}\protect\hyperlink{ref-2wDsXBwd}{87}{]}, a core resource of the community which enables live querying in the SPARQL language. {[}\protect\hyperlink{ref-dsmUPCk}{88}{]}
A number of services make use of embedded queries from the Wikidata Query Service {[}\protect\hyperlink{ref-2wDsXBwd}{87}{]} to create interactive, live dashboards like Scholia {[}\protect\hyperlink{ref-17P4zruFZ}{89}{]} and the SARS-CoV-2 Query Book {[}\protect\hyperlink{ref-guMp3q1V}{90}{]}

@@

Biomedical databases gather structured information for end users.
They are present in different states of maintenance, and reconciling cell-oriented databases to Wikidata has the potential to increase interoperability, and multiply the value of previous biocuration efforts.
PanglaoDB {[}\protect\hyperlink{ref-M0lqRYJb}{134}{]} {[}\protect\hyperlink{ref-T3PlZ3Vh}{135}{]} is a publically-available database that contains data and metadata on hundreds of single-cell RNA sequencing experiments.
It provides extensive information on cell types, genes, tissues, and cell type markers, obtained via automatic and manual methods.
It also displays a rich web user interface for easy data acquisition, including database dumps for bulk downloads.

As of 8 December June 2021, the article describing PanglaoDB had been cited 230 times.
Despite its use by the community, the database is on a 3-star category for Linked Open Data {[}\protect\hyperlink{ref-OGXYtGZ8}{136}{]} as it does not use the open semantic standards from W3C (RDF and SPARQL) needed for a 4-star rank, neither the links to external data via standard identifiers that make datasets 5-star.
Improving the data format is a valuable step in making biological knowledge FAIR (Findable, Accessible, Interoperable, and Reusable).
Thus, we provide a case study of making PandlaoDB available in a 5-star Linked Open Data Format on Wikidata.

As of August 2020, Wikidata had 264 items categorized as a ``cell type'', considerably less than the Cell Ontology, which counts over two thousand cell types {[}\protect\hyperlink{ref-agnqfdk6}{52},\protect\hyperlink{ref-4AEy2xhQ}{137}{]}.
Strikingly, there were also 23 items categorized as instances of ``cell (Q7868)''.
This classification is imprecise, as an instance of cell would be an individual named cell from a single named individual, an example of conceptual disarray that often occurs on Wikidata. {[}\protect\hyperlink{ref-imSZTi52}{138}{]}

Wikidata editors often mix 1st-order classes such as ``cells'' and ``organs'' with metaclasses like ``cell types'' and ``organ types''.
As mentioned in the chapter on the concept of cell type and Multi Level Theory, individuals, like the ``Dolly sheep zygote'' and the ``brain of Albert Einstein'' are instances of classes like ``zygote'' and ``brain'', respectively.
Classes, like ``zygote'' and ``brain'' are instances of \emph{metaclasses}, like ``cell type'' or ``organ type''.

@@

Classes corresponding to species-neutral classes were curated from Wikidata using Wikidata's Graphic User Interface.
A manually-curated dictionary matching terms in PanglaoDB to Wikidata identifiers was assembled and used for integration.
Cell types that were not represented on Wikidata were added to the database via the graphical user interface (\url{https://www.wikidata.org/wiki/Special:NewItem}) and logged in the reference table.

@@

\hypertarget{overview-of-integrated-information-on-wikidata}{%
\subsubsection{Overview of integrated information on Wikidata}\label{overview-of-integrated-information-on-wikidata}}

@@

Besides integration with Gene Ontology, Wikidata reconciliation connects the marker gene info on PanglaoDB with disease markers.

Disease genes are often compiled from Genomic Wide Association Studies, which look for sequence variation in the DNA.
These studies are commonly blind to the cell types related to the pathophysiology of the disease.
In the query below, we can see cell types marked by genes genetically associated with Parkinson's disease.
Even considering the false positives, the overview can aid domain experts in coming up with novel hypotheses.

@@

The reading framework of Wikidata bib is built upon a git repository integrated with GitHub, Python 3 scripts and SPARQL queries.
It has a standard file structure, summarized as the following:

@@

The next years of study will be devoted to improving the projects presented here into mature, useful objects.
We hope to improve the interplay of Wikidata and Cell Ontology, developing frameworks to combine community- and expert-based curation of knowledge on cell types.
Furthermore, we plan to integrate Wikidata to current single-cell RNA-sequencing pipelines by adapting R packages to use Wikidata (e.g.~the ontology-based packages OnClass {[}\protect\hyperlink{ref-sW6aNZJB}{56}{]} and ontoProc{[}\protect\hyperlink{ref-15YmDXALp}{57}{]}).
Finally, we aim at moving the Wikidata Bib system to a well documented, user-friendly mature system, testing usability with other academics and distributing it as a durable open-source project.

@@

\begin{itemize}
\tightlist
\item
  (Feb-2021) Presented an open talk at the ``Semana da Bioinformática'' event about modelling of biological systems (1020 views as of December 2021) {[}\protect\hyperlink{ref-url}{\textbf{url?}}``https://www.youtube.com/watch?v=VDvCxskIGEI''{]}
\item
  (Jun-Aug 2021) Helped to organize the No-Budget-Science HackWeek virtual hackathon {[}\protect\hyperlink{ref-12LOzmXRs}{164}{]}
\item
  (Jul - 2021) Presented the work ``Wikidata for 5-star Linked Open Databases: A case study of PanglaoDB'' at the Bio-Ontologies section of the Annual International Conference on Intelligent Systems for Molecular Biology. {[}\protect\hyperlink{ref-doi:10.5281ux2fzenodo.5747849}{\textbf{doi:10.5281/zenodo.5747849?}}{]}. The presentation was awarded the best
\item
  (Jul - 2021) Awarded the 2nd place in the International Society for Computational Biology (ISCB) Wikipedia Competition for the contributions to the Wikipedia page on Biocuration (\url{https://en.wikipedia.org/wiki/Biocuration}) {[}\protect\hyperlink{ref-IJG65hFm}{165}{]}
\item
  (Nov - 2021) Managed a project during BioHackathon Europe 2021, in Barcelona, Spain, on the representation of ELIXIR information on Wikidata. {[}\protect\hyperlink{ref-14Wi842eZ}{166}{]}
\end{itemize}

@@

\leavevmode\vadjust pre{\hypertarget{ref-ogAGO9KH}{}}%
\CSLLeftMargin{33. }
\CSLRightInline{\textbf{The origin and evolution of cell types}
\CSLBlock{Detlev Arendt, Jacob M Musser, Clare VH Baker, Aviv Bergman, Connie Cepko, Douglas H Erwin, Mihaela Pavlicev, Gerhard Schlosser, Stefanie Widder, Manfred D Laubichler, Günter P Wagner} \emph{Nature Reviews Genetics} (2016-12) \url{https://doi.org/f9b62x}
\CSLBlock{DOI: \href{https://doi.org/10.1038/nrg.2016.127}{10.1038/nrg.2016.127} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27818507}{27818507}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-g74dZjOM}{}}%
\CSLLeftMargin{38. }
\CSLRightInline{\textbf{Species Concepts and Species Delimitation}
\CSLBlock{Kevin De Queiroz} \emph{Systematic Biology} (2007-12-01) \url{https://doi.org/c34kzf}
\CSLBlock{DOI: \href{https://doi.org/10.1080/10635150701701083}{10.1080/10635150701701083} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/18027281}{18027281}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-gAysgnsS}{}}%
\CSLLeftMargin{40. }
\CSLRightInline{\textbf{Logical Development of the Cell Ontology}
\CSLBlock{Terrence F Meehan, Anna Maria Masci, Amina Abdulla, Lindsay G Cowell, Judith A Blake, Christopher J Mungall, Alexander D Diehl} \emph{BMC Bioinformatics} (2011-12) \url{https://doi.org/c7kw6x}
\CSLBlock{DOI: \href{https://doi.org/10.1186/1471-2105-12-6}{10.1186/1471-2105-12-6} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/21208450}{21208450} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3024222}{PMC3024222}}}

\leavevmode\vadjust pre{\hypertarget{ref-17U3pGEjv}{}}%
\CSLLeftMargin{41. }
\CSLRightInline{\textbf{The Cell Ontology 2016: enhanced content, modularization, and ontology interoperability}
\CSLBlock{Alexander D Diehl, Terrence F Meehan, Yvonne M Bradford, Matthew H Brush, Wasila M Dahdul, David S Dougall, Yongqun He, David Osumi-Sutherland, Alan Ruttenberg, Sirarat Sarntivijai, \ldots{} Christopher J Mungall} \emph{Journal of Biomedical Semantics} (2016-12) \url{https://doi.org/gg99b9}
\CSLBlock{DOI: \href{https://doi.org/10.1186/s13326-016-0088-7}{10.1186/s13326-016-0088-7} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27377652}{27377652} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4932724}{PMC4932724}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-jX2ZmXcc}{}}%
\CSLLeftMargin{43. }
\CSLRightInline{\textbf{Cells in experimental life sciences - challenges and solution to the rapid evolution of knowledge}
\CSLBlock{Sirarat Sarntivijai, Alexander D Diehl, Yongqun He} \emph{BMC Bioinformatics} (2017-12) \url{https://doi.org/gg99b7}
\CSLBlock{DOI: \href{https://doi.org/10.1186/s12859-017-1976-2}{10.1186/s12859-017-1976-2} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29322916}{29322916} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5763506}{PMC5763506}}}

\leavevmode\vadjust pre{\hypertarget{ref-rK8KD0us}{}}%
\CSLLeftMargin{44. }
\CSLRightInline{\textbf{Cells in ExperimentaL Life Sciences (CELLS-2018): capturing the knowledge of normal and diseased cells with ontologies}
\CSLBlock{Sirarat Sarntivijai, Yongqun He, Alexander D Diehl} \emph{BMC Bioinformatics} (2019-04) \url{https://doi.org/gg99b8}
\CSLBlock{DOI: \href{https://doi.org/10.1186/s12859-019-2721-9}{10.1186/s12859-019-2721-9} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31272374}{31272374} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6509796}{PMC6509796}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-dsmUPCk}{}}%
\CSLLeftMargin{88. }
\CSLRightInline{\textbf{Getting the Most out of Wikidata: Semantic Technology Usage in Wikipedia's Knowledge Graph, Getting the Most Out of Wikidata: Semantic Technology Usage in Wikipedia's Knowledge Graph}
\CSLBlock{Stanislav Malyshev, Markus Krötzsch, Larry González, Julius Gonsior, Adrian Bielefeldt} \emph{The Semantic Web -- ISWC 2018: 17th International Semantic Web Conference, Monterey, CA, USA, October 8--12, 2018, Proceedings, Part II} (2018-01-01) \url{https://www.wikidata.org/wiki/Q56010228}
\CSLBlock{DOI: \href{https://doi.org/10.1007/978-3-030-00668-6_23}{10.1007/978-3-030-00668-6\_23}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-P1EnNa7Q}{}}%
\CSLLeftMargin{110. }
\CSLRightInline{\textbf{The LOTUS Initiative for Open Natural Products Research: Knowledge Management through Wikidata}
\CSLBlock{Adriano Rutz, Maria Sorokina, Jakub Galgonek, Daniel Mietchen, Egon Willighagen, Arnaud Gaudry, James G Graham, Ralf Stephan, Roderic Page, Jiří Vondrášek, \ldots{} Pierre-Marie Allard} \emph{Bioinformatics} (2021-03-01) \url{https://doi.org/gh6dqk}
\CSLBlock{DOI: \href{https://doi.org/10.1101/2021.02.28.433265}{10.1101/2021.02.28.433265}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-uCE45Jh8}{}}%
\CSLLeftMargin{127. }
\CSLRightInline{\textbf{Towards a pragmatic definition of cell type}
\CSLBlock{Tiago Lubiana, Helder I Nakaya} \emph{Preprints} (2021-01-04) \url{https://doi.org/ghrxwf}
\CSLBlock{DOI: \href{https://doi.org/10.22541/au.160979530.02627436/v1}{10.22541/au.160979530.02627436/v1}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-T3PlZ3Vh}{}}%
\CSLLeftMargin{135. }
\CSLRightInline{\textbf{PanglaoDB: a web server for exploration of mouse and human single-cell RNA sequencing data}
\CSLBlock{Oscar Franzén, Li-Ming Gan, Johan LM Björkegren} \emph{Database} (2019-01-01) \url{https://doi.org/ggkzxr}
\CSLBlock{DOI: \href{https://doi.org/10.1093/database/baz046}{10.1093/database/baz046} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/30951143}{30951143} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6450036}{PMC6450036}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-MxIeSJYt}{}}%
\CSLLeftMargin{156. }
\CSLRightInline{\textbf{fcoex: FCBF-based Co-Expression Networks for Single Cells}
\CSLBlock{Tiago Lubiana, Helder Nakaya} \emph{Bioconductor version: Release (3.14)} (2022) \url{https://bioconductor.org/packages/fcoex/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-oXMFSv5v}{}}%
\CSLLeftMargin{161. }
\CSLRightInline{\textbf{Sharing intermediate datasets from systematic reviews}
\CSLBlock{Tiago Lubiana, Olavo Bohrer Amaral, Kleber Neves} \emph{MetaArXiv} (2021-11-26) \url{https://doi.org/gnrf9v}
\CSLBlock{DOI: \href{https://doi.org/10.31222/osf.io/vbwa9}{10.31222/osf.io/vbwa9}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-IJG65hFm}{}}%
\CSLLeftMargin{165. }
\CSLRightInline{\textbf{Biocuration - Wikipedia} \url{https://en.wikipedia.org/wiki/Biocuration}}

\leavevmode\vadjust pre{\hypertarget{ref-14Wi842eZ}{}}%
\CSLLeftMargin{166. }
\CSLRightInline{\textbf{biohackathon-projects-2021/projects/32 at main · elixir-europe/biohackathon-projects-2021}
\CSLBlock{GitHub} \url{https://github.com/elixir-europe/biohackathon-projects-2021}}
